Clustering time series based on probability distributions across temporal granularities

### 2021-11-14 main.Rmd
fixing sindex plot

```{r tsne-fit}

```{r tsne-plot}
```

@@

```{r opt-cluster-tsne-jsd-png, fig.cap = "(a) shows t-SNE summary of the $24$ selected customers chosen through prototype selection, (b) and (c) shows a plot of sindex for different cluster size for clustering based on JS-based distances and wpd-distances respectively. The plot suggests optimal number of clusters as $4$ and $7$ respectively."}
include_graphics("figs/opt_clust_parenthesis.png")
```

>>>>

@@

```{r tsne-fit}
```

```{r tsne-df}
```

```{r tsne-xy}

```{r opt-cluster-tsne-jsd, fig.cap = "(a) shows t-SNE summary of the $24$ selected customers chosen through prototype selection, (b) and (c) shows a plot of sindex for different cluster size for clustering based on JS-based distances and wpd-distances respectively. The plot suggests optimal number of clusters as $4$ and $7$ respectively."}
#include_graphics("figs/opt_clust_parenthesis.png")
```
